---
title: "More NN"
output: html_notebook
---
In Parts 1 and 2, I explored basic statistical models and a first try at a NN using an embedding process to capture to relationship between the high dimensional categorical variables (champions on a team). I will now attempt to develop a neural network which can accept both teams input and try to make a more accurate team victory classifier just based on champions. Due to the high variance nature of league of legends, I wouldn't expect such a network to be able to achieve a success of over 60%. Perhaps if there was more data of just high level gameplay (diamond+) there could be a sufficiently accurate discrimination of win probability based on champion compositions. That being said, with such a large range of skill, we should be able to identify large scale trends. I will also explore an SVM classifier.

# Packages
```{r}
library(tidyverse)
library(data.table)
library(keras)
library(tfruns)
library(rsample)
library(e1071)
```

# Load Data
```{r}
data.raw <- read_csv("../data/teamNames.csv")
gameInfo <- read_csv("../data/matchData.csv")
```

# Wrangle Data
```{r}
data.NN <- left_join(
  data.raw %>% 
    filter(row_number() %% 2 == 1) %>% 
    rename(team_1 = team),
  data.raw %>% 
    filter(row_number() %% 2 == 0) %>% 
    rename(team_2 = team) %>% 
    select(!win),
  by = "match"
)

data.NN

data.NN.tier <- data.NN %>% 
  left_join(
    gameInfo %>% 
      distinct(match, tier),
    by = "match"
  )

data.NN.tier
```
```{r}
data.SVM.temp <- gameInfo %>% 
  select(match, tier, championName, win) %>% 
  group_by(match) %>% 
  mutate(
    team = rleid(win),
    team = case_when(
      team == 1  ~  "Blue",
      team == 2  ~  "Red",
    ),
    championName = str_c(championName, team, sep = "_"),
    value = 1
  ) %>% 
  ungroup()
  

data.SVM <- data.SVM.temp %>% 
  distinct(match, tier, .keep_all = TRUE) %>% 
  select(match, tier, win) %>% 
  left_join(
    data.SVM.temp %>% 
      filter(team == "Blue") %>%
      select(match, championName, team, value) %>% 
      pivot_wider(
        names_from = championName,
        values_from = value
      ) %>% 
      select(!team) %>% 
      replace(is.na(.), 0),
    by = "match"
  ) %>% 
  left_join(
    data.SVM.temp %>% 
      filter(team == "Red") %>%
      select(match, championName, team, value) %>% 
      pivot_wider(
        names_from = championName,
        values_from = value
      ) %>%
      select(!team) %>% 
      replace(is.na(.), 0),
    by = "match"  
  ) %>% 
  rename(blue_win = win)

data.SVM
```
# Run an SVM
## Training and Test Data
```{r}
SVM.split <- initial_split(data.SVM %>% select(!match) %>% select(!tier), prop = 4/5)
SVM.train <- training(SVM.split)
SVM.test <- testing(SVM.split)
```

```{r}
SVM_model <- svm(
  x = SVM.train %>% select(!blue_win),
  y = as.numeric(SVM.train$blue_win),
  gamma = 1/2
)
```

```{r}
SVM_model
```
```{r}
SVM_predict <- predict(SVM_model, SVM.test %>% select(!blue_win))
mean(SVM_predict)
```



# Run Model 1
## Diagnostics
```{r}
summary(model)
```
## Tuning Runs
```{r}
runs <- tuning_run(
  "Model1.R", 
  flags = list(
    dropout = c(0.2, 0.3, 0.4, 0.5),
    unit = c(8, 16, 64)
  )
)

runs %>% 
  as_tibble() %>% 
  arrange(desc(metric_val_accuracy))
# Best accurace with .4 dropout and 8
```
## Results
```{r}
results1
```
About a .5% accuracy increase by adding enemy team comps.
## Predict
```{r}
predict(model, list("TahmKench Graves Veigar Jihn Lux", "Jayce Viego Kayle Kaisa Nami"))
```
## Saving
```{r}
save_model_tf(model, "initialModel.tf")
```

# Run Model 2
## Results
```{r}
results2
```


