---
title: "League of Legends Analysis"
output: html_notebook
---
# Introduction
Like most league of legends players, I have a love / hate relationship with this game. I love the game to death, but playing it is an absolute nightmare. Feeding into this dynamic is partially the champion balance, or lack thereof, in this game which leads to frustrations on my part. In an effort to better understand champion balance I wanted to do a few things:

1. Understand how winrate is affected by vision score and establish quick rules of thumb for appropriate vision scores by game time.
2. Why certain champions have low winrates and derive practical recommendations for players.
3. Apply unsupervised statistical learning techniques to model and understand team compositions and winning factors that can be analyzed before the game starts. 

# Run Order
1. DataExtraction.RMD
2. BasicStatisticalModels.RMD
3. ChampionStatistics.RMD
4. TreeSVM.RMD
5. NeuralNetwork.RMD

# Acknowledgements
A lot of this code is based off of reddit user u/WallabyKingdom's work, so shouts out for laying the groundwork for me to springboard off of.

# Packages
```{r message = F}
library(tidyverse)
library(jsonlite)
library(httr)
library(rvest)
```

# API Key (hidden)
```{r include = F}
# api <- "hidden"
```

# List for storing data
```{r}
# Don't run again or else the global environment will be cleared
# matchData <- list()
# data.temp <- list()
```


# Getting champion id keys and tidying data
```{r}
#champions.raw <- fromJSON("http://ddragon.leagueoflegends.com/cdn/11.10.1/data/en_US/championFull.json")

champions <- as_tibble(do.call(rbind, champions.raw$data)) %>% 
  select(id, key, tags, info) %>% 
  mutate(
    info = map(
      info,
      .f = function(info){
  
        info %>% 
          as_tibble() %>%
          return()
  
      }
    ),
    tag1 = map(
      tags,
      .f = function(tags){
        
        tags[[1]] %>% 
          return()
        
      }
    ),
    tag2 = map(
      tags,
      .f = function(tags){
        
        if(length(tags) == 1){
          
          return(NA_character_)
          
        }else{
          
        tags[[2]] %>% 
          return()
          
        }
      }
    )
  ) %>%
  unnest(cols = c(id, key, info, tag1, tag2)) %>% 
  mutate(key = as.integer(key)) %>% 
  select(!tags)
# Tags will be used downstream (maybe? hopefully... ?_?)
head(champions)
# Note Rell and Seraphine have no stats
```

# Mobalytics Champions
```{r}
# I noticed Akshan wasn't present, so I'm going to make a secondary champion list by scraping a Mobalytics page
# Note this relys on scraping data first so this chunk is out of sequential order
mobalytics.raw <- read_html("https://app.mobalytics.gg/lol/champions")

data.temp$championNames <- mobalytics.raw %>% # I can scrape the actual league matches
  html_elements(".m-1xem6pd") %>% 
  html_text()

data.temp$championDifficulty <- mobalytics.raw %>% 
  html_elements("p") %>% 
  html_text() %>% 
  {.[2:158]}

data.temp$championTag <- mobalytics.raw %>% 
  html_elements(".m-1br68c5") %>%
  html_attr(name = "alt")

champions.scraped <- tibble(
  name = gameInfo %>% 
    distinct(championName) %>% 
    mutate(
      championName = case_when(
        championName == "MonkeyKing"  ~  "Wukong", 
        TRUE                          ~  championName # For whatever reason riot calls wukong monkey king which messes with the ordering of the mobalytics data
      )
    ) %>% 
    arrange(championName) %>% 
    {.$championName},
  tag = data.temp$championTag,
  difficulty = data.temp$championDifficulty %>% 
    factor(levels = c("Easy", "Average", "Hard", "Severe"))
) %>% 
  mutate(
      name = case_when(
        name == "Wukong"  ~  "MonkeyKing",
        TRUE              ~  name
    )
  ) %>% 
  arrange(name)

# champions %>% 
#   filter(
#     !(id %in% champions.scraped$name)
#   )
# Seriously, why is fiddlesticks the only one what is different, whatever doesn't matter, the info gotten from the .json is clearly outdated.
```


# Item Data 
```{r}
# Might use this later maybe not
items.raw <- fromJSON("https://raw.githubusercontent.com/InFinity54/LoL_DDragon/master/latest/data/en_US/item.json")
```

# Retrieving Match Data
## First prepare inputs
```{r}
data.temp$tier <- c("IRON", "BRONZE", "SILVER", "GOLD", "PLATINUM", "DIAMOND")
data.temp$division <- c("I", "II", "III", "IV")

data.temp$tier_div <- expand_grid(data.temp$tier, data.temp$division) %>% 
  rename(tier = 1, division = 2)
```

## Write function to extract summoner id's
```{r}
RIOTAPI_FUNCTIONS <- list()

GET_JSON <- function(INPUT){
  
  output <- GET(INPUT) # Have to use httr::GET to properly parse this url
  
  output$content %>% 
    rawToChar() %>% 
    fromJSON() %>% 
    return()
  
}

RIOTAPI_FUNCTIONS$GET_ACCOUNTS <- function(tier, division){
  
  Sys.sleep(1.2)
  url <- paste0("https://na1.api.riotgames.com/lol/league/v4/entries/RANKED_SOLO_5x5/", tier, "/", division, "?page=1&api_key=", api)
  
  GET_JSON(url) %>% 
    return()
  
}

RIOTAPI_FUNCTIONS$GET_PUUID <- function(summonerId){
  
  Sys.sleep(1.2)
  url <- paste0("https://na1.api.riotgames.com/lol/summoner/v4/summoners/", summonerId,  "?api_key=", api)
  
  GET_JSON(url) %>% 
    return()
  
}

RIOTAPI_FUNCTIONS$GET_HISTORY <- function(puuid){
  
  Sys.sleep(1.2)
  url <- paste0("https://americas.api.riotgames.com/lol/match/v5/matches/by-puuid/", puuid, "/ids?queue=420&start=0&count=20&api_key=", api)
  
  GET_JSON(url) %>% 
    return()
  
}

RIOTAPI_FUNCTIONS$GET_MATCH <- function(matchid){
  
  Sys.sleep(1.2)
  url <- paste0("https://americas.api.riotgames.com/lol/match/v5/matches/", matchid, "?api_key=", api)
  
  GET_JSON(url) %>% 
    return()
  
}
```

## Execute function
```{r}
# Doing this in steps because of the api query request limitations
# First get summonerIds
matchData$accounts.raw <- data.temp$tier_div %>%
  mutate(
    accounts = pmap(
      .,
      .f = RIOTAPI_FUNCTIONS$GET_ACCOUNTS
    )
  )
```
```{r}
# Just retaining the summonerIds
matchData$summonerIds <- matchData$accounts.raw %>% 
  mutate(
    accounts = map(
      accounts,
      .f = function(accounts){
        accounts %>%
          select(summonerId) %>%
          return()
      }
    )
  ) %>% 
  unnest(cols = accounts)
```
```{r}
# Get PUUID's now, need this to get match history
matchData$accounts <- matchData$summonerIds %>% 
  mutate(
    puuid = map(
      summonerId,
      .f = RIOTAPI_FUNCTIONS$GET_PUUID
    ),
    puuid = map( # Probably separate this next time just in case maybe? It might work fine with the select function
      puuid,
      .f = function(puuid){
        puuid %>% 
          as_tibble() %>% 
          select(puuid) %>% 
          return()
      }
    )
  ) %>%
  unnest(puuid)

head(matchData$accounts)
```

## Getting Match History from puuid
```{r}
matchData$match_history <- matchData$accounts %>% 
  mutate(
    matches = map(
      puuid,
      .f = RIOTAPI_FUNCTIONS$GET_HISTORY
    )
  )

head(matchData$match_history)
```
```{r}
matchData$matches <- matchData$match_history %>% 
  mutate(
    empty = map(
      matches,
      .f = is_empty
    )
  ) %>% 
  unnest(cols = empty) %>%
  filter(empty == FALSE) %>% 
  unnest(cols = matches) %>% 
  distinct(matches, .keep_all = T) %>% 
  select(tier, division, match = matches)

head(matchData$matches)
```

## Getting match information
```{r}
# splitting into two because of the api key expiration
matchData$gameInfo.low <- matchData$matches %>% 
  filter(tier %in% c("IRON", "BRONZE", "SILVER")) %>% 
  mutate(
    gameInfo = map(
      match,
      .f = RIOTAPI_FUNCTIONS$GET_MATCH
    )
  )

matchData$gameInfo.high <- matchData$matches %>% 
  filter(tier %in% c("GOLD", "PLATINUM", "DIAMOND")) %>% 
  mutate(
    gameInfo = map(
      match,
      .f = RIOTAPI_FUNCTIONS$GET_MATCH
    )
  )
```

## Tidying up data
```{r}
matchData$gameInfo.raw <- bind_rows(
  matchData$gameInfo.low,
  matchData$gameInfo.high
) %>% 
  mutate(
    version = map(
      gameInfo,
      .f = function(gameInfo){
        
        gameInfo$info$gameVersion %>% 
          return()
        
      }
    ),
    gameInfo = map(
      gameInfo,
      .f = function(gameInfo){
        
        gameInfo$info$participants %>% 
          return()
        
      }
    )
  ) %>% 
  unnest(cols = c("version", "gameInfo"))

gameInfo <- matchData$gameInfo.raw %>% # Selecting only certain columns for simplicity
  select(tier, division, version, match, assists, champExperience, champLevel, championId, championName, deaths, detectorWardsPlaced, firstBloodKill, goldEarned, goldSpent, individualPosition, item1, item2, item3, item4, item5, item6, kills, lane, role, timePlayed, totalDamageDealtToChampions, totalDamageDealt, totalTimeSpentDead, visionScore, wardsKilled, wardsPlaced, win) %>% 
  mutate(
    tier = factor(tier, levels = c("IRON", "BRONZE", "SILVER", "GOLD", "PLATINUM", "DIAMOND")),
    division = factor(division, levels = c("I", "II", "III", "IV")),
    individualPosition = factor(individualPosition, levels = c("UTILITY", "BOTTOM", "MIDDLE", "JUNGLE", "TOP", "Invalid")),
    lane = factor(lane, levels = c("BOTTOM", "MIDDLE", "JUNGLE", "TOP", "NONE")),
    role = factor(role, levels= c("SUPPORT", "CARRY", "NONE", "SOLO", "DUO")),
    timePlayed = timePlayed / 60,
    win = factor(win, levels = c(FALSE, TRUE))
  )

gameInfo.noInvalid <- gameInfo %>% filter(individualPosition != "Invalid")
```

Finally we have our match info! This is an absurdly large data set, so I may prune it a bit. Setting Iron I, and Support / Bot Lane to be the baseline (Somewhat biased as an adc/support main).

# Saving
```{r}
write_csv(gameInfo, "../data/matchData.csv")
save(gameInfo, champions.scraped, file = "../data/league.RDATA")
```
